### 2009-12-15 doc/tech_doc/a-rex/arex_tech_doc.tex
Information about transfer shares added to the A-REX manual

\begin{itemize}
\item \textbf{Accepted} -- In this state the job has been submitted to a
CE but is not processed yet. The A-REX will analyze the JD and move
to the next stage. If the JD can not be processed the job will be
canceled and moved to the state \textbf{Finishing}.
\item \textbf{Preparing} -- The input data is being gathered in the SD (stage-in).
The A-REX is downloading the files specified in the JD and is waiting
for files which are supposed to be uploaded by the UI. If all files
are successfully gathered the job moves to the next state. If \textbf{any}
file can't be downloaded or it takes the UI too long to upload a file,
the job moves to \textbf{Finishing} state. It is possible to put a
limit on the number of simultaneous \textbf{Preparing} jobs. If this
limit is exceeded, jobs ready to enter the \textbf{Preparing} state
 will stay in the \textbf{Accepted} state, but prefixed with the PENDING:
mark. Exceptions are jobs which have no files to be downloaded. These
are processed out of limits.
\item \textbf{Submitting} -- The job is being passed for execution to the
\emph{Local Resource Management System} (LRMS). The corresponding
backends for many LRMSs are provided with the default installation.
If the local job submission is successful the job moves to the \textbf{Executing}
state. Otherwise it moves to \textbf{Finishing}. It is possible to
limit the aggregate number of jobs in \textbf{Submitting} and \textbf{Executing}
states.
\item \textbf{Executing} -- The job is queued or being executed in the LRMS.
The A-REX takes no actions except waiting until the job finishes.
\item \textbf{Killing} -- Necessary action to cancel the job in the LRMS
is being taken.
\item \textbf{Finishing} -- The output data is being processed (stage-out).
Specified data files are moved to the specified SEs and are optionally
registered at an Indexing Service. The user can download data files
from the SD by using the UI or other adequate tool. All the files
not specified as output files are removed from the SD at very beginning
of this state. It is possible to limit number of simultaneous jobs
in this state.
\item \textbf{Finished} -- No more processing is performed by the A-REX.
The user can continue to download data files from the SD. The SD is
kept available for some time (default is 1 week). After that the job
is moved to the state \textbf{Deleted}. The 'deletion' time can be
obtained by querying the Information Interface of the A-REX. If a
job was moved to \textbf{Finished} because of failure, it may be restarted
on request of a client. When restarted, a job is moved to the state
previous to the one in which it failed and is assigned mark PENDING.
This is needed in order to not break the configuration limits. Exception
is a job failed in \textbf{Executing} state and lacking input files
specified in JD. Such a job is treated like failed in \textbf{Preparing}
state.
\item \textbf{Deleted} -- The job is moved to this state if the user have
not requested job to be cleaned before the SD's lifetime expires.
Only minimal subset of information about such job is kept. The SD
is not available anymore.
\end{itemize}
In case of a failure special processing is applied to output files.
All specified output files are treated as \textbf{downloadable by
the user}. No files will be moved to their destination SE.

@@

\begin{itemize}
\item \textit{subject} -- user certificate's subject, also known as the distinguished
name (DN)
\item \textit{starttime} -- GMT time when the job was accepted represented
in the Generalized Time format of LDAP 
\item \textit{lifetime} -- time period to preserve the SD after the job has
finished in seconds
\item \textit{cleanuptime} -- GMT time when the job should be removed from
the cluster and it's SD deleted in Generalized Time format
\item \textit{notify} -- email addresses and flags to send mail to about
the job specified status changes
\item \textit{processtime} -- GMT time when to start processing the job in
Generalized Time format
\item \textit{exectime} -- GMT time when to start job execution in Generalized
Time format
\item \textit{expiretime} -- GMT time when the credentials delegated to the
job expire in Generalized Time format
\item \textit{rerun} -- number of retries left to rerun the job
\item \textit{jobname} -- name of the job as supplied by the user
\item \textit{projectname} -- name of the project as supplied by the user
\item \textit{lrms} -- name of the LRMS backend to be used for local submission
\item \textit{queue} -- name of the queue to run the job at
\item \textit{localid} -- job id in LRMS (appears only after the job has
reached state \textbf{InLRMS})
\item \textit{globalid} -- BES ActivityIdentifier XML tree, the global
identifier of the job
\item \textit{args} -- executable name followed by a list of command-line
arguments
\item \textit{downloads} -- number of files to download into the SD before
execution
\item \textit{uploads} -- number of files to upload from the SD after execution
\item \textit{gmlog} -- directory name which holds files containing information
about the job when accessed through GridFTP interface
\item \textit{clientname} -- name (as provided by the user interface) and
IP address:port of the submitting client machine
\item \textit{clientsoftware} -- version of software used to submit the job
\item \textit{sessiondir} -- the job's SD
\item \textit{failedstate} -- state in which job failed (available only if
it is possible to restart the job)
\item \textit{jobreport} -- URL of a user requested \emph{logger service}.
The A-REX will also send job records to this service in addition to
the default logger service configured in the configuration.
\item \textit{activityid} -- Job-id of previous job in case the job has been 
resubmitted or migrated. This value can appear multiple times if a job has been 
resubmitted or migrate more than once.
\item \textit{forcemigration} -- This boolean is only used for migration of jobs.
It determines whether the job should persist if the termination of the previous 
job fails.
\end{itemize}

@@

@@

>>>>

\begin{itemize}
\item \textbf{Accepted} -- In this state the job has been submitted to a
CE but is not processed yet. The A-REX will analyze the JD and move
to the next stage. If the JD can not be processed the job will be
canceled and moved to the state \textbf{Finishing}.
\item \textbf{Preparing} -- The input data is being gathered in the SD (stage-in).
The A-REX is downloading the files specified in the JD and is waiting
for files which are supposed to be uploaded by the UI. If all files
are successfully gathered the job moves to the next state. If \textbf{any}
file can't be downloaded or it takes the UI too long to upload a file,
the job moves to \textbf{Finishing} state. It is possible to put a
limit on the number of simultaneous \textbf{Preparing} jobs. 
If this limit is exceeded, jobs ready to enter the \textbf{Preparing} state
 will stay in the \textbf{Accepted} state, but prefixed with the PENDING:
mark. Exceptions are jobs which have no files to be downloaded. These
are processed out of limits.
\item \textbf{Submitting} -- The job is being passed for execution to the
\emph{Local Resource Management System} (LRMS). The corresponding
backends for many LRMSs are provided with the default installation.
If the local job submission is successful the job moves to the \textbf{Executing}
state. Otherwise it moves to \textbf{Finishing}. It is possible to
limit the aggregate number of jobs in \textbf{Submitting} and \textbf{Executing}
states.
\item \textbf{Executing} -- The job is queued or being executed in the LRMS.
The A-REX takes no actions except waiting until the job finishes.
\item \textbf{Killing} -- Necessary action to cancel the job in the LRMS
is being taken.
\item \textbf{Finishing} -- The output data is being processed (stage-out).
Specified data files are moved to the specified SEs and are optionally
registered at an Indexing Service. The user can download data files
from the SD by using the UI or other adequate tool. All the files
not specified as output files are removed from the SD at very beginning
of this state.It is possible to limit the number of simultaneous jobs in this state.
\item \textbf{Finished} -- No more processing is performed by the A-REX.
The user can continue to download data files from the SD. The SD is
kept available for some time (default is 1 week). After that the job
is moved to the state \textbf{Deleted}. The 'deletion' time can be
obtained by querying the Information Interface of the A-REX. If a
job was moved to \textbf{Finished} because of failure, it may be restarted
on request of a client. When restarted, a job is moved to the state
previous to the one in which it failed and is assigned mark PENDING.
This is needed in order to not break the configuration limits. Exception
is a job failed in \textbf{Executing} state and lacking input files
specified in JD. Such a job is treated like failed in \textbf{Preparing}
state.
\item \textbf{Deleted} -- The job is moved to this state if the user have
not requested job to be cleaned before the SD's lifetime expires.
Only minimal subset of information about such job is kept. The SD
is not available anymore.
\end{itemize}
In case of a failure special processing is applied to output files.
All specified output files are treated as \textbf{downloadable by
the user}. No files will be moved to their destination SE.

@@

\begin{itemize}
\item \textit{subject} -- user certificate's subject, also known as the distinguished
name (DN)
\item \textit{starttime} -- GMT time when the job was accepted represented
in the Generalized Time format of LDAP 
\item \textit{lifetime} -- time period to preserve the SD after the job has
finished in seconds
\item \textit{cleanuptime} -- GMT time when the job should be removed from
the cluster and it's SD deleted in Generalized Time format
\item \textit{notify} -- email addresses and flags to send mail to about
the job specified status changes
\item \textit{processtime} -- GMT time when to start processing the job in
Generalized Time format
\item \textit{exectime} -- GMT time when to start job execution in Generalized
Time format
\item \textit{expiretime} -- GMT time when the credentials delegated to the
job expire in Generalized Time format
\item \textit{rerun} -- number of retries left to rerun the job
\item \textit{jobname} -- name of the job as supplied by the user
\item \textit{projectname} -- name of the project as supplied by the user
\item \textit{lrms} -- name of the LRMS backend to be used for local submission
\item \textit{queue} -- name of the queue to run the job at
\item \textit{localid} -- job id in LRMS (appears only after the job has
reached state \textbf{InLRMS})
\item \textit{globalid} -- BES ActivityIdentifier XML tree, the global
identifier of the job
\item \textit{args} -- executable name followed by a list of command-line
arguments
\item \textit{downloads} -- number of files to download into the SD before
execution
\item \textit{uploads} -- number of files to upload from the SD after execution
\item \textit{gmlog} -- directory name which holds files containing information
about the job when accessed through GridFTP interface
\item \textit{clientname} -- name (as provided by the user interface) and
IP address:port of the submitting client machine
\item \textit{clientsoftware} -- version of software used to submit the job
\item \textit{sessiondir} -- the job's SD
\item \textit{failedstate} -- state in which job failed (available only if
it is possible to restart the job)
\item \textit{jobreport} -- URL of a user requested \emph{logger service}.
The A-REX will also send job records to this service in addition to
the default logger service configured in the configuration.
\item \textit{activityid} -- Job-id of previous job in case the job has been 
resubmitted or migrated. This value can appear multiple times if a job has been 
resubmitted or migrate more than once.
\item \textit{forcemigration} -- This boolean is only used for migration of jobs.
It determines whether the job should persist if the termination of the previous 
job fails.
\item \textit{transfershare} -- name of share used in \textbf{Preparing}
and \textbf{Finishing} states.
\end{itemize}

@@

\item \textbf{\textit{maxloadshare}}\textit{=max\_share share\_type} -- specifies a 
sharing mechanism for data transfer. \emph{max\_share} is the maximum
number of processes that can run per transfer share and \emph{share\_type} is 
the scheme used to assign jobs to transfer shares. See Section~\ref{sub:Transfershare}
for possible values and more details.

@@

\subsection{Transfer shares\label{sub:Transfershare}}

For many jobs, large amounts of input and output data can mean
significant time is spent in the PREPARING and FINISHING states
gathering input data and writing output data. With FIFO processing,
this can lead to one user or group of users blocking the queue for
others. The A-REX implements a sharing system to avoid this problem, by
assigning each user or group of users to a ``transfer share'' and
specifying a limit on the number of data transfer processes per
share. If one user's jobs' transfer share is using the maximum number
of processes and another user submits jobs which are assigned to a
different share, the second user's jobs can immediately go to
PREPARING, up to the same maximum limit of processes. This means that
no matter how many jobs the first user submits, the second user's jobs
are not blocked. Assuming the bandwidth from the sources of input data
for both users' jobs is similar, the available throughput will then be
split evenly between the two users' jobs.

If a limit on the total number of data transfer processes is set in
the \emph{maxload} option, the maximum number of processes per
transfer share is set by splitting the total maximum evenly among all
the shares with jobs in data transfer states, up to the maximum
allowed per share.

The scheme used to assign jobs to transfer shares can be set in the
\emph{maxloadshare} option. Possible values are:

\begin{itemize}
\item \emph{dn} - each job is assigned to a share based on the DN of
  the user sumbitting the job.
\item \emph{voms:vo} - if the user's proxy is a VOMS~\cite{voms} proxy
  the job is assigned to a share based on the VO specified in the
  proxy. If the proxy is not a VOMS proxy a default share is used.
\item \emph{voms:role} - if the user's proxy is a VOMS proxy the job
  is assigned to a share based on the role specified in the first
  attribute found in the proxy. If the proxy is not a VOMS proxy a
  default share is used.
\item \emph{voms:group} - if the user's proxy is a VOMS proxy the job is
  assigned to a share based on the group specified in the first
  attribute found in the proxy. If the proxy is not a VOMS proxy a
  default share is used.
\end{itemize}

If VOMS is not supported, the \emph{dn} scheme is the only option that
should be used, as using a VOMS-based scheme will lead to all jobs
being assigned to the default share.

\textbf{Important:} If a sharing mechanism based on VOMS is used,
server certificates for each supported VO must be installed. It is
possible to either download the public key of each VOMS server, or
create a special file for each VO containing the server's DN and its
CA DN. Instructions are given on NorduGrid's web site at
\url{http://www.nordugrid.org/documents/voms-notes.html}.
